The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

Chart about factors that affect entrepreneurship.
Source: OECD Local Entrepreneurship Reviews
Strentghening Entrepreneurship and economic development in East Germany: Lessons from local approaches.
![here](https://github.com/SamDund/Assign2Education/blob/master/Untitled.png)

@@

>>>>

Chart about factors that affect entrepreneurship.
Source: OECD Local Entrepreneurship Reviews
Strengthening entrepreneurship and economic development in East Germany: Lessons from local approaches.
![here](https://github.com/SamDund/Assign2Education/blob/master/Untitled.png)

@@

"Self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).
